Many Analystis Project

### 2022-02-08 analysis.Rmd
Update analysis.Rmd

---
title: "Many Analystis Project"
description: 
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-APRIL-29 
bibliography: references.bib
link-citations: true
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
    highlight: kate
---

@@

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

```{r cache = TRUE}
# clean data:use informative names !

# note from Suzanne: 
# I do think it's actually a negative relation, as the anxiety item was reverse-coded (following the documentation from the WHO quality of life scale, from which the items were taken). This is indicated in the data documentation, but I can totally understand this got buried under all information that was provided. We tried to make the dataset as clean as possible since most teams just aggregated all well-being items (and the religiosity items). But in retrospect, this recoding did cause some confusion for a couple of teams that used only specific items (and prefered the ordinal scale). This is definitely something to take into account for future projects like this one.

@@

dg1 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) #%>%#%>%
 # tidy_dagitty()       
# 
dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")

@@

```{r}
library(lme4)

@@

d1ipwB <- ipw::ipwpoint(
  exposure = bg_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  ch_s + age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipwB$ipw.weights)
sum(d1ipwB$ipw.weights > 10)

d1pB <- d1 %>% 
  mutate(ipw = d1ipwB$ipw.weights) %>%
  filter(ipw < 10)
```

@@

```{r}
mgeeB  <- geeglm(
  anx ~
    bg_s,# + # already weighted
   # ch_s +
   # age_s  +
   # male,
  data = d1pB,
  id = country,
  weights = ipw
)

@@

d1p <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights)
```

@@

```{r, eval = FALSE}

# trim IPW to less than 10 
d1pf <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)

@@

```{r, cache = TRUE}
library(viridis)
p0<-brms::conditional_effects(m1, "bg_s", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical = T,
                              prob = .89,
                              method = 'fitted')

>>>>

---
title: "Many Analystis Project"
description: 
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-APRIL-29 
bibliography: references.bib
link-citations: true
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
    highlight: kate
editor_options: 
  chunk_output_type: console
---

@@

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

```{r cache = TRUE}
# clean data:use informative names !
# note from Suzanne: 
# I do think it's actually a negative relation, as the anxiety item was reverse-coded (following the documentation from the WHO quality of life scale, from which the items were taken). This is indicated in the data documentation, but I can totally understand this got buried under all information that was provided. We tried to make the dataset as clean as possible since most teams just aggregated all well-being items (and the religiosity items). But in retrospect, this recoding did cause some confusion for a couple of teams that used only specific items (and prefered the ordinal scale). This is definitely something to take into account for future projects like this one.

@@

dg1 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events",
    coords = list(x = c(anx =6 , 
                        belief = 5, 
                        church = 4, 
                        ses = 3,
                        male = 2, 
                        age = 2,
                        country = 2,
                        U = 1),
                  y = c(anx = 2, 
                        belief = 2, 
                        church = 2, 
                        ses = 2,
                        male = 2, 
                        age = 2,
                        country = 1,
                        U = 1)) #%>%#%>%
 # tidy_dagitty()       
# 
dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")

@@

```{r}
library(lme4)
```

@@

First check for imbalance using the cobolt package.

```{r}
# CHECK BALANCE
# test
cobalt::bal.tab(bg_s ~ age_s  + male + country,
        data = d1, estimand = "ATE", m.threshold = .05)
```

Get inverse probability weights

```{r}
w_out_bs <- weightit(bg_s ~ age_s  +ch_s +  male + country,
        data = d1, estimand = "ATE", method = "ebal", stabilize = TRUE)
w_out_bs

summary(w_out_bs)
sum(w_out_bs$weights)

cobalt::bal.tab(w_out_bs, m.threshold = .05, disp.v.ratio = TRUE)
```

```{r}
library("ipw")
d1ipwB <- ipw::ipwpoint(
  exposure = bg_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  ch_s + age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipwB$ipw.weights)
sum(d1ipwB$ipw.weights >= 10)

d1pB <- d1 %>% 
  mutate(ipw = w_out_bs$weights) %>%
  filter(d1ipwB$ipw.weights < 10)

@@

```{r}
mgeeB  <- geeglm(
  anx ~
    bg_s,# already weighted
   # ch_s +
   # age_s  +
   # male,
  data = d1pB,
  id = country,
  corstr = "exchangeable",
  weights = ipw
)
mgeeB

@@

d1p <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)
```

@@

```{r, eval = FALSE}
# trim IPW to less than 10 
d1pf <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)

@@

```{r, cache = TRUE}
library(viridis)
p0<-brms::conditional_effects(m1, "bg_s", 
                              spaghetti = T,
                              ndraws = 500,
                              categorical = F,
                              prob = .89,
                              method = 'fitted')
